\documentclass{article} \usepackage{listings}

\usepackage{url} % URL is used to display a link

\lstset{
    basicstyle={\ttfamily\small},
    frame=tRBl,
    framesep=10pt,
    breaklines=true,
    linewidth=12cm,
    lineskip=-0.5ex,
    tabsize=2 
}

\title{Practical Course on Parallel Computing  Hands-on Exercise}
\author{Dr. Gen Kawamura - gen.kawamura@cern.ch}

\begin{document}
\maketitle


Submission Deadline: 27.04.2018. Write your commnets in the source codes. Send both codes and outpus to a Tutor, Gen Kawamura.





%-----------------------------------------
% Hello World
%-----------------------------------------
\section{Posix Thread: Basis}
Let's start Pthreads.\\ 
\\
The following codes can generate the first Pthreads examples in the lecture. Write and compile the codes and run the executables.
\footnote{The codes will be available on the lecture page later - :\url{https://studip.uni-goettingen.de/dispatch.php/course/files/index/5b7ccc78b7e0fef55991d2112bd230da?cid=380bcd4f6ebf1551d43071e799bcb23d}}。\\

\begin{itemize}
\item Hello World {\it basic.c}
\lstinputlisting[language=C++]{codes/basic.c}

\item Excecusion of basic.c
\begin{lstlisting}
$ gcc -pthread basic.c -o basic 
$ ./basic
\end{lstlisting}


\item With pthread arguments: {\it answer.c}
\lstinputlisting[language=C++]{codes/answer.c}

\item With many pthread arguments: {\it hello\_arg2.c}
\lstinputlisting[language=C++]{codes/hello_arg2.c}

\end{itemize}


%-----------------------------------------
% Shared Data
%-----------------------------------------
\section{Shared Data}
The global C variables in the following codes are global over thread boundaries.

\begin{itemize}

\item Basic example for shared data: {\it basic\_glob\_var.c}
\lstinputlisting[language=C++]{codes/basic_glob_var.c}

\item A mutex example using dotprod (serial ver.): {\it dotprod\_serial.c}
\lstinputlisting[language=C++]{codes/dotprod_serial.c}

\item A Mutex example using dotprod (threadable ver.): {\it dotprod\_mutex.c}
\lstinputlisting[language=C++]{codes/dotprod_mutex.c}

\end{itemize}


%-----------------------------------------
% Signaling and Condition Variables
%-----------------------------------------
\section{Signaling and Condition Variables}
With a condition variable it can signal another thread about an event, e.g. that they are finished doing something.

\begin{itemize}

\item Signaling and Condition Variables: {\it condvar.c}
\lstinputlisting[language=C++]{codes/condvar.c}

%% The barrier.c code is relying on the older C99 syntax
%\item Example of barrier: {\it barrier.c}
%\lstinputlisting[language=C++]{codes/barrier.c}


\end{itemize}

%-----------------------------------------
% Signaling and Condition Variables
%-----------------------------------------
\section{Performance - Bug}

This example code contains a bug. Please find and fix it.

\begin{itemize}
\item A buggy code: Where is the bug? {\it bug6.c}
\lstinputlisting[language=C++]{codes/bug6.c}


\end{itemize}


\end{document}
